---
output:
  md_document:
    variant: markdown_github
bibliography: actigraph.bib
---
[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/TheTS/actigraph.sleepr?branch=master&svg=true)](https://ci.appveyor.com/project/TheTS/actigraph-sleepr)
[![Travis-CI Build Status](https://travis-ci.org/TheTS/actigraph.sleepr.svg?branch=master)](https://travis-ci.org/TheTS/actigraph.sleepr)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/actigraph.sleepr)](https://cran.r-project.org/package=actigraph.sleepr)
[![minimal R version](https://img.shields.io/badge/R%3E%3D-3.2.4-6666ff.svg)](https://cran.r-project.org/)
[![packageversion](https://img.shields.io/badge/Package%20version-0.1.0-orange.svg?style=flat-square)](commits/master)
[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-yellowgreen.svg)](/commits/master)
[![codecov](https://codecov.io/gh/TheTS/actigraph.sleepr/branch/master/graph/badge.svg)](https://codecov.io/gh/TheTS/actigraph.sleepr)

<!-- README.md is generated from README.Rmd. Please edit that file -->

### actigraphr: Non-wear, sleep, and physical activity analysis from ActiGraph data

```{r, echo = FALSE}
knitr::opts_chunk$set(collapse = TRUE, 
                      comment = "#>",
                      fig.path = "README-")
```

The `actigraphr` package is used to analyse accelerometer data obtaiend from ActiGraph devices. It includes several non-wear, sleep, and physical activity detection algorithms. 

* Non-wear detection algorithms: Troiano [@Troiano:2008aa] and Choi [@Choi:2011aa]
* Sleep scoring algorithms: Sadeh [@Sadeh:1994aa], Cole-Kripke [@Cole:1992aa] and Tudor-Locke [@Tudor-Locke:2014aa], 
* Physical activity cutpoints: Freedson adult [@Freedson:1998aa], Freedson adult VM [@Freedson:2011aa], Freedson children [@Freedson:2005aa], Evenson children [@Evenson:2008aa], Mattocks  children [@Mattocks:2007aa], and Puyau children [@Puyau:2002aa].


This package is an extension of the [`actigraph.sleepr` package](https://github.com/dipetkov/actigraph.sleepr).

### Installation

```{r, eval = FALSE}
library("devtools")
install_github("TheTS/actigraphr")
```

### References
