---
output:
  md_document:
    variant: markdown_github
bibliography: actigraph.bib
---
[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
[![Travis-CI Build Status](https://travis-ci.org/TheTS/actigraph.sleepr.svg?branch=master)](https://travis-ci.org/TheTS/actigraphr)
[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-yellowgreen.svg)](/commits/master)
[![codecov](https://codecov.io/gh/TheTS/actigraphr/branch/master/graph/badge.svg)](https://codecov.io/gh/TheTS/actigraphr)

<!-- README.md is generated from README.Rmd. Please edit that file -->

### actigraphr: Non-wear, sleep, and physical activity analysis from ActiGraph data

```{r, echo = FALSE}
knitr::opts_chunk$set(collapse = TRUE, 
                      comment = "#>",
                      fig.path = "README-")
```

The `actigraphr` package is used to analyse accelerometer data obtaiend from ActiGraph devices. It includes several non-wear, sleep, and physical activity detection algorithms. 

This package extends the [`actigraph.sleepr`](https://github.com/dipetkov/actigraph.sleepr) package, written by Desislava Petkova.

Non-wear detection algorithms:

  * Troiano [@Troiano:2008aa]
  * Choi [@Choi:2011aa]
  
Sleep scoring algorithms:

  * Sadeh [@Sadeh:1994aa]
  * Cole-Kripke [@Cole:1992aa]
  * Tudor-Locke [@Tudor-Locke:2014aa]
  
Physical activity thresholds:

  * Freedson adult [@Freedson:1998aa]
  * Freedson adult VM [@Freedson:2011aa]
  * Freedson children [@Freedson:2005aa]
  * Evenson children [@Evenson:2008aa]
  * Mattocks  children [@Mattocks:2007aa]
  * Puyau children [@Puyau:2002aa]


### Installation

```{r, eval = FALSE}
library("devtools")
install_github("TheTS/actigraphr")
```

### Examples

`actigraphr` supports reading AGD files and raw gt3x files that are exported from the Actilife software.

```{r include=FALSE}
library(actigraphr)

agd_file <- system.file("extdata", "GT3XPlus-RawData-Day01.agd",
                        package = "actigraphr")

agdb <- read_agd(agd_file)
```

When an AGD file is read, the information about the device settings are saved as attributes:

```{r}
str(agdb)
```

This file can then be processed using the dplyr pipe syntax. This snippet collapses the data to 30 second epochs, before adding weartime and physicay activity intensity columns:

```{r}
scored <- agdb %>% 
  collapse_epochs(60) %>% 
  apply_weartime(fun = apply_troiano) %>% 
  apply_cutpoints(cutpoints = "evenson_children") 
```

```{r eval=FALSE}
head(scored, 5)
```

```{r echo=FALSE}
knitr::kable(head(scored, 5))
```

Summarising this data over a specified time interval (e.g. daily, hourly) is as simple as:

```{r}
summary <- scored %>% 
  summarise_agd(time = "1 hour")
```

And this summary information can then be plotted:

```{r, fig.width=8, fig.height=4}
plot_activity_summary(summary)
```

*More documentation and vignettes to come!*

### References
